Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/normalsandcurvature.tex
true normals and error graphs

\begin{figure}

\end{figure}

>>>>

\begin{figure}
    \begin{tikzpicture}
        \centering
        \begin{axis}[
            width=0.8\textwidth,
            xlabel={Gridstep},
            ylabel={RMSE error},
            x dir=reverse,
            legend pos=north east,
            ymajorgrids=true,
            grid style=dashed,
            ymode=log,
            xmode=log,
            log ticks with fixed point,
        ]
            \addplot[
                color=cyan,
            ] coordinates {
                (0.125,0.0133408)(0.250,0.0146335)(0.375,0.0178744)(0.500,0.0236486)(0.625,0.0337591)(0.750,0.0408107)(0.875,0.0461201)(1.000,0.0561247)
            };
            \addlegendentry{ellipsoid};
            \addplot[
                color=red,
            ] coordinates {
                (0.125,0.0230513)(0.250,0.0221659)(0.375,0.0396149)(0.500,0.0588389)(0.625,0.0738491)(0.750,0.0919486)(0.875,0.105444)(1.000,0.103468)
            };
            \addlegendentry{goursat};
        \end{axis}
    \end{tikzpicture}
    \caption{RMSE error as a function of Grid Resolution}
    \label{fig:errorl2-gridstep}
\end{figure}

\begin{figure}
    \begin{tikzpicture}
        \centering
        \begin{axis}
            [
            width=0.8\textwidth,
            xlabel={Gridstep},
            ylabel={$E_{\max}$ error},
            x dir=reverse,
            legend pos=north east,
            ymajorgrids=true,
            grid style=dashed,
            ymode=log,
            xmode=log,
            log ticks with fixed point,
            ]
            \addplot[
                color=cyan,
            ] coordinates {
                (0.125,0.0688766)(0.250,0.0581494)(0.375,0.0503613)(0.500,0.0501076)(0.625,0.085362)(0.750,0.0821788)(0.875,0.120426)(1.000,0.102295)
            };
            \addlegendentry{ellipsoid}
            \addplot[
                color=red,
            ] coordinates {
                (0.125,0.116514)(0.250,0.0554448)(0.375,0.111164)(0.500,0.144318)(0.625,0.186091)(0.750,0.151117)(0.875,0.213926)(1.000,0.197462)
            };
            \addlegendentry{goursat}
        \end{axis}
    \end{tikzpicture}
    \caption{$E_{\max}$ error as a function of Grid Resolution}
    \label{fig:errorloo-gridstep}
\end{figure}
